Enhancing Adversarial Robustness for Deep Metric Learning

### 2021-10-15 robdml.tex
u

Note, the design of HM is flexible, and not coupled with specific sampling
strategy.
%
In other words, any existing or future triplet sampling strategy can
be adopted in HM.

@@

@@

@@

>>>>

Note, the design of HM is flexible, and not coupled with specific sampling
strategy.
%
In other words, any existing or future triplet sampling strategy can
be adopted in HM.
%
or even a pseudo hardness function $g(\cdot)$ as long as we have a strong
prior knowledge on what the destination hardness should be.

@@

strong example when the embedding space is not in good shape.

@@

\begin{equation}
	%
	g_\mathsf{B}(H(\cdots)) = H(\cdots) + \xi \cdot \bar{\ell}_{t-1}
	%
\end{equation}

\begin{equation}
	%
	g_\mathsf{SGA}() = -\gamma \cdot \bar{\ell}_{t-1}
	%
\end{equation}

@@

This section is organized in logical order where a group of experiments
or ablation study
provides clues for the next group of experiment.
%
Hence, the comparison to the state-of-the-art works are put at the last
subsection.
